Scalar Items in Embedded Position: {A}n Experimental Revisit

### 2012-11-26 text/paper/paper2.tex
results/discussion - changes

@@

In order to test whether accentuation or the quantifier has an
influence on the distribution of readings, log-liner models were
computed (see Schepers 2003). The factors {\it Reading}, {\it
  Accentuation} and {\it Quantifier} were included in these
models. Two variants of these models were computed.  In the first, the
factor {\it Item} was added to the above mentioned. In the latter {\it
  Participants} was included as a factor. Inclusion of these two
factors allowed us to test whether the distribution of readings was
identical accros items and participants. We report log-likelihood
ratio Chi-squares ($LRCS_1$ and $LRCS_2$), degrees of freedom ($df_1$,
$df_2$) and significance levels ($p_1$ and $p_2$).

@@

Participants' judgments are depicted in Figures \ref{Fig:EC_judgments} and 
\ref{Fig:LC_judgments}. Judgments were coded as \ec or as \lc if they were as expected
under one of these readings, and as "other" if they were not. The distributions 
of readings thus coded is illustrated in Figure \ref{fig:response-type-freque-TRF}. 
Overall, participants mainly gave answers corresponding to the \lc-reading (65\%). 
Moreover, the preference for this reading was constrained by prosody. When prosody 
supported a dispreferred \ec-reading, the number of \lc-decisions was decreased. In both 
\lc- and \ec-sequences, the number of \lc-answers was highest when this reading
was supported by prosodic phrasing (i.e. 77\%  and 76\%, respectively), and a bit lower
with neutral prosody (69\%  and 63\%). This clearcut advantage decreased when prosodic
phrasing supported the \ec-reading (52\%  vs. 56\%). The number 
of erroneous answers did not differ between the single conditions. Finally, the
availability of readings within a sequence did not yield any significant effects.

In order to test statistically whether prosodic phrasing and sequential ordering 
had an effect on the number of \lc choices, log-linear models with the factors
{\it Reading}, {\it Prosody}, {\it Sequence}, {\it Item}, and {\it Participant} were included.

An effect of {\it Reading} reflects that overall, readings were distributed inhomogeneously
($LRCS = 539.04, p < .001$). As revealed by an interaction between {\it Prosody} and
{\it Reading}, prosodic phrasing had an influence upon the distribution of readings 
($LRCS = 50.42, p < .001$). Finally, an interaction between {\it Participant} and {\it Reading}
shows that readings were distributed unevenly amongst participants ($LRCS = 345.22, p < .001$)

@@

\subsection{Interpretation}
\label{sec:interpretation}

High scores of success clearly indicate that participants understood 
the incremental verification task and were in general able to give 
judgements at the earliest possible point in a picture sequence. 
Moreover, results obtained for the preference-related controls  
show that our design is able to detect multiple readings and preferences 
among these. Crucially, the amount of response types for \lc- and \ec-readings 
reflected the known preference for the former, \emph{irrespective} of the 
order in which each reading could first be judged in a given sequence. 
Finally, prosodic effects were restricted to the preference-related 
controls. As expected, the dispreferred \ec-reading was chosen 
significantly more often when supported by prosodic phrasing. Interestingly, 
contrastively accenting scalar \emph{some} had no effect on the observed 
decisions in \as- and \es-sentences.

@@

\subsection{Discussion}
\label{sec:discussion}

>>>>

In the following, we will report the results for targets and positional
controls separately. After providing the descriptive results, we present
statistical analyses, which were carried out in the following manner.
We computed log-liner models (see Scheepers 2003) in two variants (by 
item and by participant). In the first, the factor {\it Item} was 
included, and in the second analysis, the factor {\it Participants} 
was included. Inclusion of these two factors allowed us to test whether 
the distribution of participants' choices was identical accros items and 
participants. We report log-likelihood ratio Chi-squares ($LRCS_1$ 
and $LRCS_2$), degrees of freedom ($df_1$, $df_2$) and significance 
levels ($p_1$ and $p_2$). The relevant experimental
factors are provided in the specific subsections below.

@@

In order to test whether accentuation or the quantifier has an
influence on the distribution of readings, log-liner models 
including the factors {\it Reading}, {\it Accentuation} and 
{\it Quantifier}.

@@

Participants' judgments are depicted in Figures \ref{Fig:EC_judgments} and 
\ref{Fig:LC_judgments}. Judgments were coded as \ec or as \lc if they were as expected
under one of these readings, and as "other" if they were not. The distributions 
of readings thus coded is illustrated in Figure \ref{fig:response-type-freque-TRF}. 
Overall, participants mainly gave answers corresponding to the \lc-reading (65\%). 
Moreover, this pattern was constrained by prosody. When prosody 
supported a dispreferred \ec-reading, the number of \ec-decisions were increased.

In both \lc- and \ec-sequences, the number of \ec-answers was highest when this reading
was supported by prosodic phrasing (i.e. 30\%  and 32\%, respectively), and a bit lower
with neutral prosody (24\%  and 25\%). When prosodic phrasing supported the \lc-reading,
the number of \ec choices was lowest (12\% in both sequences). The number 
of erroneous answers did not differ between the single conditions. Finally, the
availability of readings within a sequence did not yield any significant effects.

In order to test statistically whether prosodic phrasing and sequential ordering 
had an effect on the number of \ec-choices, we contrasted the number of \ec-choices
with non-\ec -choices (i.e. \lc-answers and erroneous responses together), calculating
log-linear model analyses with the factors {\it Reading}, {\it Prosody}, and 
{\it Sequence}.

An effect of {\it Reading} reflects that overall, readings were distributed inhomogeneously
($LRCS_1 = 252.8, df_1 =1, p_1 < .001$; $LRCS_2 = 252.8, df_2 =1, p_2 < 001$). 
As revealed by an interaction between {\it Prosody} and
{\it Reading}, prosodic phrasing had an influence upon the distribution of readings 
($LRCS_1 = 38.4, df_1 =2, p_1 < 001$; $LRCS_2 = 26.1, df_2 =2, p_2 < .001$).

In the analysis by participant, an interaction between {\it Participant} and {\it Reading}
indicates that reading preferences differed between participants ($LRCS_1 = 376.6,df_1 =37,  
p_1 < .001$).

In the analysis by items, a three-way interaction between {\it Item}, {\it Prosody} and 
{\it Reading} was observed ($LRCS_2 = 88.3, df_1 =54, p_2 < .01$). As this effect was 
unexpected, we carried out additional descriptive analyses (crosstables) in order to examine whether
the interaction might have been caused by specific items. When excluding the four items with
the highest deviation from expected frequencies (Residuals > 2.4 in at least one cell), 
the interaction was no longer significant ($p_2 = .18$).

@@

\subsection{Discussion}
\label{sec:interpretation}

High scores of success clearly indicate that participants understood 
the incremental verification task and were in general able to give 
judgements at the earliest possible point in a picture sequence. 
Moreover, results obtained for the preference-related controls  
show that our design is able to detect multiple readings and preferences 
among these. Crucially, the amount of response types for \lc- and \ec-readings 
reflected the known preference for the former, \emph{irrespective} of the 
order in which each reading could first be judged in a given sequence.
Finally, the incremental verification task was generally sensitive
to prosody. However, prosodic effects were restricted to the preference-related 
controls. As expected, in these conditions, the dispreferred \ec-reading was chosen 
significantly more often when supported by prosodic phrasing. Interestingly, 
contrastively accenting scalar \emph{some} had no effect on the observed 
decisions in the target conditions. Crucially, local readings occurred in both
\as- and \es-sentences, independently of prosody. Finally, closer examination of 
the participants' decisions revealed two groups: participants in the first
group consistently gave answers corresponding to local readings, whereas participants
in the second group consistently showed a literal interpretation.

@@

\subsection{General Discussion}
\label{sec:discussion}
